\centerline{Sudoku}

### 2021-05-25 report/paper.tex
Add very important pictures and show that we can solve the world's hardest sudoku
Signed-off-by: Joey <bevilacquajoey@gmail.com>

\section{Trials} \label{trials}
%%%%%
\bibliographystyle{abbrv}
\bibliography{references}

>>>>

\section{Trials}\label{trials}

\begin{figure}
\caption{The web app UI}
\centering
\includegraphics[width=0.8\textwidth]{pics/app_ui.png}
\end{figure}

\begin{figure}
\caption{Fill the sudoku board}
\centering
\includegraphics[width=0.8\textwidth]{pics/fill_board.png}
\end{figure}

\begin{figure}
\caption{Press the \texttt{Solve} button to find the soluscion}
\centering
\includegraphics[width=0.8\textwidth]{pics/solved.png}
\end{figure}

\begin{figure}
\caption{Errors if a number appears multiple times in the same row}
\centering
\includegraphics[width=0.8\textwidth]{pics/row_check.png}
\end{figure}

\begin{figure}
\caption{Errors if a number appears multiple times in the same column}
\centering
\includegraphics[width=0.8\textwidth]{pics/column_check.png}
\end{figure}

\begin{figure}
\caption{Errors if a number appears multiple times in the same box}
\centering
\includegraphics[width=0.8\textwidth]{pics/box_check.png}
\end{figure}

\begin{figure}
\caption{Errors if a number is not in $ \left[ 1, 9 \right] $}
\centering
\includegraphics[width=0.8\textwidth]{pics/column_check.png}
\end{figure}

\begin{figure}
\caption{Errors if a number is not in $ \left[ 1, 9 \right] $}
\centering
\includegraphics[width=0.8\textwidth]{pics/input_check.png}
\end{figure}

\begin{figure}
\caption{Solve \href{https://www.mirror.co.uk/news/weird-news/worlds-hardest-sudoku-can-you-242294}{the world's hardest sudoku} in seconds}
\centering
\includegraphics[width=0.8\textwidth]{pics/hardest_sudoku.png}
\end{figure}

%%%%%
\bibliographystyle{abbrv}
\bibliography{references}
